### 2024-08-10 README.Rmd
Fixed copy-edit error

On November 30, 2022, OpenAI released what became its flagship product, [ChatGPT](https://en.wikipedia.org/wiki/ChatGPT), a chatbot based on [Large Language Models](https://en.wikipedia.org/wiki/Large_language_model) (LLMs) designed and trained to mimic natural language. The launch of the chatbot was an impressive feat of marketing [@cowen_chatgpt_2023]. It took less than two weeks for the hype to reach stratospheric levels, and by early December it had opinion-makers raving: not only was ChatGPT "the best artificial intelligence chatbot ever released to the general public" [@roose_brilliance_2023], some wondered whether it could even "replace humans" with its "impressively detailed" and "human-like" text "replace humans" [@lock_what_2022].

>>>>

On November 30, 2022, OpenAI released what became its flagship product, [ChatGPT](https://en.wikipedia.org/wiki/ChatGPT), a chatbot based on [Large Language Models](https://en.wikipedia.org/wiki/Large_language_model) (LLMs) designed and trained to mimic natural language. The launch of the chatbot was an impressive feat of marketing [@cowen_chatgpt_2023]. It took less than two weeks for the hype to reach stratospheric levels, and by early December it had opinion-makers raving: not only was ChatGPT "the best artificial intelligence chatbot ever released to the general public" [@roose_brilliance_2023], some even wondered whether it could "replace humans" with its "impressively detailed" and "human-like" text [@lock_what_2022].
